---
output: github_document
---

### Confidence intervals of heterogeneity parameters in the "Association Between Administration of IL-6 Antagonists and Mortality Among Patients Hospitalized for COVID-19" article
#### Arthur M. Albuquerque, Donald R. Williams and James M. Brophy
#### July 23, 2021

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this document, we present the estimated confidence intervals of $I^2$ estimates
derived from the article ["Association Between Administration of IL-6 Antagonists and Mortality Among Patients Hospitalized for COVID-19"](https://jamanetwork.com/journals/jama/fullarticle/2781880).

We fitted random-effect meta-analyses to estimate heterogeneity parameters with
three different estimators:

* Restricted maximum-likelihood estimator
* DerSimonian-Laird estimator
* Hedges estimator

All models were fitted using the R package [metafor](https://wviechtb.github.io/metafor/reference/confint.rma.html). 

#### Load data

```{r message=FALSE, warning=FALSE}
# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

pacman::p_load(rio, # import data
               here, # reproducible file paths
               dplyr, # to use %>%
               metafor) # fit meta-analyses

d = import(here("figure1_data.xlsx"))

# Calculate effect sizes for each study
d_or = escalc(measure = "OR",
              ai = trt_events, n1i = trt_total,
              ci = control_events, n2i = control_total,
              slab= study,
              data = d)
```

## Restricted maximum-likelihood estimator

#### Pooled tocilizumab and sarilumab

```{r}
rma(yi, vi, data=d_or, method = "REML") %>% 
  confint(digits = 1)
```

The estimated $I^2$ was 16.6% (95% confidence interval [CI] 0 - 58.5).

#### Tocilizumab

```{r}
rma(yi, vi, data=d_or, subset=(treatment=="tocilizumab"),
    method = "REML") %>% 
  confint(digits = 1)
```

The estimated $I^2$ was 0% (95% CI 0 - 71.2).

#### Sarilumab

```{r}
rma(yi, vi, data=d_or, subset=(treatment=="sarilumab"),
    method = "REML") %>% 
  confint(digits = 1)
```

The estimated $I^2$ was 0% (95% CI 0 - 80.1).

## DerSimonian-Laird estimator

#### Pooled tocilizumab and sarilumab

```{r}
rma(yi, vi, data=d_or, method = "DL") %>% 
  confint(digits = 1)
```

The estimated $I^2$ was 1.2% (95% CI 0 - 58.5).

#### Tocilizumab

```{r}
rma(yi, vi, data=d_or, subset=(treatment=="tocilizumab"),
    method = "DL") %>% 
  confint(digits = 1)
```

The estimated $I^2$ was 0% (95% CI 0 - 71.2).

#### Sarilumab

```{r}
rma(yi, vi, data=d_or, subset=(treatment=="sarilumab"),
    method = "DL") %>% 
  confint(digits = 1)
```

The estimated $I^2$ was 0% (95% CI 0 - 80.1).

## Hedges estimator

#### Pooled tocilizumab and sarilumab

```{r}
rma(yi, vi, data=d_or, method = "HE") %>% 
  confint(digits = 1)
```

The estimated $I^2$ was 0% (95% CI 0 - 58.5).

#### Tocilizumab

```{r}
rma(yi, vi, data=d_or, subset=(treatment=="tocilizumab"),
    method = "HE") %>% 
  confint(digits = 1)
```

The estimated $I^2$ was 0% (95% CI 0 - 71.2).

#### Sarilumab

```{r}
rma(yi, vi, data=d_or, subset=(treatment=="sarilumab"),
    method = "HE") %>% 
  confint(digits = 1)
```

The estimated $I^2$ was 0% (95% CI 0 - 80.1).

